### 2024-06-25 basic-statistics.qmd
20240624 - fixes

where $R^2_{\text{model}$ is the $R^2$ of the model with the [predictor variable](#sec-correlationalStudy) of interest and R^2_{\text{reduced}} is the $R^2$ of the model without the [predictor variable](#sec-correlationalStudy) of interest.

@@

#### ANOVA {#sec-statisticalPowerANOVA}

@@

>>>>

where $R^2_{\text{model}}$ is the $R^2$ of the model with the [predictor variable](#sec-correlationalStudy) of interest and $R^2_{\text{reduced}}$ is the $R^2$ of the model without the [predictor variable](#sec-correlationalStudy) of interest.

@@

#### One-Way ANOVA {#sec-statisticalPowerOneWayANOVA}

@@

#### Factorial ANOVA {#sec-statisticalPowerFactorialANOVA}

```{r}
pwr::pwr.anova.test(
  n = N,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorA)

pwr::pwr.anova.test(
  n = N,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorB)

pwr::pwr.anova.test(
  n = N,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorA + numLevelsFactorB)
```

```{r}
pwr::pwr.anova.test(
  power = power,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorA)

pwr::pwr.anova.test(
  power = power,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorB)

pwr::pwr.anova.test(
  power = power,
  f = effectSize_f,
  sig.level = alpha,
  k = numLevelsFactorA + numLevelsFactorB)
```

```{r}
pwr::pwr.anova.test(
  power = power,
  n = N,
  sig.level = alpha,
  k = numLevelsFactorA)

pwr::pwr.anova.test(
  power = power,
  n = N,
  sig.level = alpha,
  k = numLevelsFactorB)

pwr::pwr.anova.test(
  power = power,
  n = N,
  sig.level = alpha,
  k = numLevelsFactorA + numLevelsFactorB)
```
